ML parameters

### 2023-03-17 workflow/notebooks/ml-params.Rmd
Rerender ml-params
Plot trainfrac

---
title: "ML parameters"
date: "`r Sys.Date()`"
output: 
  github_document:
    html_preview: false
  gfm:
    html_preview: false
---

@@

>>>>

---
title: "ML parameters"
date: "`r Sys.Date()`"
output: 
  github_document:
    html_preview: false
  gfm:
    html-preview: false
    embed-resources: true
---

@@

```{r plot_trainfrac}
results_dat %>% 
  filter(method == 'glmnet', metric == 'AUROC', taxlevel == "OTU") %>% 
  ggplot(aes(perf_metric_value, perf_metric_name, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_grid(trainfrac~dataset) +
  labs(x="performance on held out test data")
```
